\begin{thebibliography}{99}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
%%% EVERYTHING BELOW IS OLD, REVIEW AND KEEP AS NEEDED}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5




%
% THIS ITEM BELOW IS JUST A STARTER, REMOVE IT WHEN IT IS NOT NEEDED
%
% \bibitem{bib:CMSHiggs} CMS Collaboration, ``Observation of a new boson at a
%   mass of 125~GeV with the CMS experiment at the LHC,'' Phys. Lett. {\bf
%     B716} 30 (2012), \url{http://dx.doi.org/10.1016/j.physletb.2012.08.021}
\bibitem{bib:P5}
Particle Physics Project Prioritization Panel, ``Building for Discovery - Executive Summary,'' (2014), \url{http://go.unl.edu/8oyk}

\bibitem{bib:firstWandZxsec}
 %S.~Chatrchyan {\it et al.},
 CMS Collaboration, ``Measurement of the Inclusive W and Z Production 
     Cross Sections in pp Collisions at $\sqrt{s} =$7\TeV,''
     JHEP {\bf 10}, 132 (2011).
     
\bibitem{bib:smtxsec} CMS Collaboration, ``Measurement of the $t\bar{t}$
  Production Cross Section in $pp$ Collisions at 7\TeV in Lepton + Jets
  Events Using $b$-quark Jet Identification, Phys. Rev. {\bf D84} 092004
  (2011), \url{http://dx.doi.org/10.1103/PhysRevD.84.092004}.

 \bibitem{bib:Keller-thesis} J.~Keller, D.~Claes, ``TTbar Production Cross Section Measurement in the Muon Plus Jets Channel using Soft Electron Tagging in pp Collisions at $\sqrt{s}=$8~TeV," CERN-THESIS-2013-095, \url{https://cds.cern.ch/record/1569842?ln=en}.

\bibitem{bib:DY7TeV}
CMS Collaboration, ``Measurement of the differential and double-differential Drell-Yan cross sections in proton-proton collisions at $\sqrt{s} =$ 7\TeV,''
JHEP {\bf 1312}, 030 (2013), %(Oct 27, 2013)
arXiv:1310.7291 [hep-ex],
\url{http://dx.doi.org/10.1007/JHEP12(2013)030}.

\bibitem{bib:DY8TeV}
CMS Collaboration, ``Measurements of differential and double-differential Drell-Yan cross sections in proton-proton collisions at $\sqrt{s}=$8\TeV,'' 
Eur. Phys. J. C 75 (2015) 147, arXiv:1412.1115 [hep-ex], \url{http://dx.doi.org/10.1140/epjc/s10052-015-3364-2}.

\bibitem{bib:single-top-papers}
%
CMS Collaboration, ``Observation of the associated production of a single top quark and a W boson in pp collisions at $\sqrt{s}=$8\TeV,'' Phys. Rev. Lett. 112 (23), 231802 (2014), \url{http://dx.doi.org/10.1103/PhysRevLett.112.231802};
%
CMS Collaboration, ``Measurement of the t-channel single-top-quark production cross section and of the $|V_{tb}|$ CKM matrix element in pp collisions at $\sqrt{s} = 8$\TeV,'' JHEP 06 (2014) 090, \url{http://dx.doi.org/10.1007/JHEP06(2014)090};
%
CMS Collaboration, ``Measurement of the W boson helicity in events with a single reconstructed top quark in pp collisions at $\sqrt{s}=$8\TeV,''  Journal of High Energy Physics {\bf 01},  053 (2015), \url{http://dx.doi.org/10.1007/JHEP01(2015)053}.

\bibitem{bib:HWWlegacy}
CMS Collaboration, ``Measurement of Higgs boson production and properties in the WW decay channel with leptonic final states,'' JHEP {\bf 1401}, 096 (2014), arXiv:1312.1129 [hep-ex], doi:10.1007/JHEP01(2014)096.

\bibitem{bib:higgs-spin-parity}
CMS Collaboration, ``Constraints on the spin-parity and anomalous HVV couplings of the Higgs boson in proton collisions at 7 and 8\TeV, '' Phys. Rev. {\bf D92} 012004 (2015),
\url{http://dx.doi.org/10.1103/PhysRevD.92.012004}.

\bibitem{bib:tHqbbPAS} CMS Collaboration, ``Search for $H \to b\bar{b}$ in association with single top quarks as a test of Higgs boson couplings," CMS PAS HIG-14-015 (2015), \url{https://cds.cern.ch/record/1952829}

\bibitem{bib:tHqpaper} CMS Collaboration, ``Search for the associated production of a Higgs boson with a single top quark in proton-proton collisions at $sqrt{s} = 8$\TeV," submitted to Journal of High Energy Physics, CMS-HIG-14-027 (2015), \url{http://arxiv.org/abs/1509.08159}.

\bibitem{bib:Bartekthesis} R.~Bartek, R.~Clare, A.~Dominguez, ``Search for the Standard Model Higgs Boson Produced in Association with a $Z$ Boson in the Electron-Muon Final State and the Higgs Boson Decaying into Bottom Quarks,'' \url{https://cds.cern.ch/record/1605425}.
 
 \bibitem{bib:higgs-LFV}
 CMS Collaboration, ``Search for lepton-flavour-violating decays of the Higgs boson, '' Phys. Lett. {\bf B749} 337 (2015), \url{http://dx.doi.org/10.1016/j.physletb.2015.07.053}.
 
\bibitem{bib:Bsmumu} CMS Collaboration, ``Measurement of the $B^0_s \to \mu^+\mu^-$ branching fraction and search for $B^0 \to \mu^+\mu^−$ with the CMS Experiment,'' Phys. Rev. Lett. 111 101804 (2013), \url{http://dx.doi.org/10.1103/PhysRevLett.111.101804};
CMS and LHCb Collaborations, ``Observation of the rare $B^0_s \to \mu^+\mu^−$ decay from the combined analysis of CMS and LHCb data,'' Nature 14474 (2015), \url{http://dx.doi.org/10.1038/nature14474}.


\bibitem{bib:quark-compositness-etc}
CMS Collaboration, ``Search for quark contact interactions and extra spatial dimensions using dijet angular distributions in proton–proton collisions at $\sqrt{s}$8\TeV,'' Phys. Lett. {\bf B746} 79 (2015), \url{http://dx.doi.org/10.1016/j.physletb.2015.04.042}.

\bibitem{bib:bstar}
CMS Collaboration, ``Search for the production of an excited bottom quark decaying to tW in proton-proton collisions at $\sqrt{s} = 8\TeV$,'' submitted to JHEP, \url{http://arxiv.org/abs/1509.08141}.



\bibitem{bib:btagperformance} CMS Collaboration ``Identification of $b$-quark jets with the CMS experiment,'' J. Instrum. {\bf 8} P04013 (2013), \url{http://dx.doi.org/10.1088/1748-0221/8/04/P04013}.
 
\bibitem{bib:EGM-Run1-SF}
CMS Collaboration, ``Performance of electron reconstruction and selection with the CMS detector in proton-proton collisions at $\sqrt{s}=$8\TeV,'' J. Instrum. {\bf 10} P06005 (2015), \url{http://dx.doi.org/10.1088/1748-0221/10/06/P06005}.
 
\bibitem{bib:trackperf}
CMS Collaboration, ``Description and performance of track and primary vertex reconstruction with the CMS tracker,'' J.~Instrum. \textbf{9}(2014) P10009.

\bibitem{bib:alignment}
CMS Collaboration, ``Alignment of the CMS tracker with LHC and cosmic ray data,'' J.~Instrum. \textbf{9} (2014) P06009, \url{http://arxiv.org/abs/1403.2286}.

\bibitem{bib:AAA} K.~Bloom, T.~Boccali, B.~Bockelman, D.~Bradley, S.~Dasu, J.~Dost, F.~Fanzago, I.~Sfiligoi, A.~Mrak Tadel, M.~Tadel, C.~Vuosalo, F.~W\"{u}rthwein, A.~Yagil and M.~Zvada, ``Any Data, Any Time, Anywhere: Global Data Access for Science," accepted by 2nd IEEE/ACM International Symposium on Big Data Computing (2015), \url{https://arxiv.org/abs/1508.01443}.

\bibitem{bib:pixTDR}
A.~Dominguez, D.~Abbaneo, K.~Arndt, N.~Bacchetta, A.~Ball, E.~Bartz, W.~Bertl, G.M.~Bilei, G.~Bolla, H.W.K.~Cheung, M.~Chertok, S.~Costa, N.~Demaria, K.~Ecklund, W.~Erdmann, K.~Gill, G.~Hall, K.~Harder, F.~Hartmann, R.~Horisberger, W.~Johns, H.C.~Kaestli, K.~Klein, D.~Kotlinski, S.~Kwan, M.~Pesaresi, H.~Postema, T.~Rohe, C.~Sch\"{a}fer, A.~Starodumov, S.~Streuli, A.~Tricomi, P.~Tropea, J.~Troska, F.~Vasey, W.~Zeuner, ``CMS Technical Design Report for the Pixel Detector Upgrade,'' CERN-LHCC-2012-016 (2016), \url{https://cds.cern.ch/record/1481838?ln=en}

\bibitem{bib:thesisawardwebsite} \url{http://cmsthesisawards.web.cern.ch}


\bibitem{bib:slowmuons} D0 Collaboration, ``Search for Charged Massive Long-Lived Particles,” Phys. Rev. Lett. {\bf 108} 121802 (2012), \url{http://dx.doi.org/10.1103/PhysRevLett.108.121802}.

\bibitem{bib:IKheavyZ} D0 Collaboration, ``Search for a heavy neutral gauge boson in the dielectron channel with 5.4 fb$^{−1}$ of $p\bar{p}$ collisions at $\sqrt{s}=1.96$\TeV, Phys. Lett. {\bf B695} 88 (2011), \url{http://dx.doi.org/ 10.1016/j.physletb.2010.10.059}.

\bibitem{bib:dalethesis}
Dale Johnston, ``Search for the Standard Model Higgs Boson in p-pbar Interactions with the decay mode $H\rightarrow W^+ W^- \rightarrow \mu^+ \nu \mu^- \nu$ at the D0 Experiment,'' Ph.D. Dissertation, University of Nebraska -- Lincoln (2010), \url{http://digitalcommons.unl.edu/physicsdiss/9/}.

\bibitem{bib:D0lumi} B.C.K.~Casey, M.~Corcoran, K.~DeVaughan, Y.~Enari, E.~Gallas, I.~Katsanos, J.~Linnemann, J.~Orduna, R.~Partridge, M.~Prewitt, H.~Schellman, G.R.~Snow, and M.~Verzocchi, ``The D0 Run IIb Luminosity Measurement," Nucl. Instrum. Meth. {\bf A698} 208 (2013), \url{http://dx.doi.org/10.1016/j.nima.2012.08.095}.

\bibitem{bib:D0afb} D0 Collaboration, ``Forward-backward asymmetry in top quark-antiquark production,” Phys. Rev. {\bf D84} 112005 (2011), http://dx.doi.org/10.1103/PhysRevD.84.112005;
D0 Collaboration, ``Measurement of Leptonic Asymmetries and Top Quark Polarization in tt Production,'' Phys. Rev. {\bf D87} 011103(R) (2013), \url{http://link.aps.org/doi/10.1103/PhysRevD.87.011103};
D0 Collaboration, ``Measurement of the asymmetry in angular distributions of leptons produced in dilepton $t\bar{t}$ final states in $p\bar{p}$ collisions at $\sqrt{s} = 1.96$~TeV,'' Phys. Rev. {\bf D88} 112002 (2013),
\url{http://dx.doi.org/10.1103/PhysRevD.88.112002};
D0 Collaboration, ``Measurement of the forward-backward asymmetry in the distribution of leptons in $t\bar{t}$ in the lepton+jets channel,'' Phys. Rev. {\bf D90} 072001 (2014), \url{http://dx.doi.org/10.1103/PhysRevD.90.072001};
D0 Collaboration, ``Measurement of the forward-backward asymmetry in top quark-antiquark production in $p\bar{p}$ collisions using the lepton+jets channel,'' Phys. Rev. {\bf D90} 072011 (2014), \url{http://dx.doi.org/10.1103/PhysRevD.90.072011};
D0 Collaboration, ``Simultaneous measurement of forward-backward asymmetry and top polarization in dilepton final states from $t\bar{t}$ production at the Tevatron,'' Phys. Rev. {\bf D92} 052007 (2015), \url{http://dx.doi.org/10.1103/PhysRevD.92.052007}.

\bibitem{bib:RICE} I.~Kravchenko, S.~Hussain, D.~Seckel, D.~Besson,
  E.~Fensholt, J.~Ralston, J.~Taylor, K.~Ratzlaff and R.~Young, ``Updated
  Results from the RICE Experiment and Future Prospects for Ultra-High
  Energy Neutrino Detection at the South Pole,'' Phys. Rev. {\bf D85}
  062004 (2012), \url{http://dx.doi.org/10.1103/PhysRevD.85.062004}.

\bibitem{bib:ARA}
ARA Collaboration, ``First Constraints on the Ultra-High Energy Neutrino Flux from a Prototype Station of the Askaryan Radio Array,'' Astroparticle Physics 70 (2015) 62-80, arXiv:1404.5285;
%
ARA Collaboration, ``Performance of two Askaryan Radio Array stations and first results in the search for ultra-high energy neutrinos,'' arXiv:1507.08991.

\bibitem{bib:CRADAR} M.~Abou Bakr Othman, C.~Allen, J.~Belz, D.~Besson,
  B.~Farhang-Boroujeny, D.~Ikeda, S.~Kunwar, J.P.~Lundquist, I.~Kravchenko,
  I.~Myers, T.~Nakamura, H.~Sagawa, P.~Sokolsky, H.~Takai, T.~Terasawa and
  G.B.~Thomson, ``Air Shower Detection by Bistatic Radar,'' AIP Conf. Proc
  {\bf 1367} 143 (2011), \url{http://dx.doi.org/10.1063/1.3628731}.

\bibitem{bib:cropweb} \url{http://crop.unl.edu}

\bibitem{bib:bloomblog} \url{http://www.quantumdiaries.org/author/ken-bloom/}.

\bibitem{bib:TBBTQD} \url{http://www.quantumdiaries.org/2015/02/05/theory-and-experiment-come-together-bazinga/}.

\bibitem{bib:TBBTepisode} \url{http://bit.ly/16NhxDu}

\bibitem{bib:fairphotos} See photos from the Science Fairs at \url{https://www.facebook.com/Feriaauger2012/photos_stream}.

\bibitem{bib:ICRCoutreach} See for instance
``Education and Outreach in the Pierre Auger Observatory," G.~Snow for the Pierre
Auger Collaboration, Proceedings of the 33rd International Cosmic Ray Conference,
July 2013, Rio de Janeiro, Brazil, arXiv:1307.5059 [astro-ph].


\bibitem{bib:top-mass}
CMS Collaboration, ``Measurement of the top quark mass using proton-proton data at $\sqrt{s}=$7 and 8\TeV,'' arXiv:1509.04044 [hep-ex], submitted to Phys.~Rev.~D.

\bibitem{bib:carlthesis}
Carl Lundstedt, ``Search for stop squarks in $p\bar{p}$ collisions at $\sqrt{s} = 1.8$\TeV utilizing the D0 detector,'' Ph.D. Dissertation, University of Nebraska -- Lincoln (2001), \url{https://inspirehep.net/record/579223}.

\bibitem{bib:d0susy}
D0 Collaboration, ``Search for Light Top Squarks in $p\bar{p}$ Collisions at $\sqrt{s}=1.8$\TeV,'' Phys. Rev. Lett {\bf 76}, 2222 (1996);
D0 Collaboration, ``Search for First Generation Scalar Leptoquark Pairs in $p\bar{p}$ Collisions at $\sqrt{s} = 1.8$\TeV,'' Phys. Rev. {\bf D60}, 031101(R) (1999);
D0 Collaboration, ``Search for Pair Production of Light Scalar Top Quarks in $p\bar{p}$ Collisions at $\sqrt{s}=1.8$\TeV,'' Phys. Rev. Lett. {\bf 93}, 011801 (2004);
D0 Collaboration, ``Search for Squarks and Gluinos in Events with Jets and Missing Transverse Energy in $p\bar{p}$ Collisions at $\sqrt{s}=1.96$\TeV,'' Phys. Lett. {\bf B638}, 119 (2006).

\bibitem{bib:phase2}
CMS Collaboration, ``Technical Proposal for the Phase-II Upgrade of the CMS Detector,'' CERN-LHCC-2015-010 (2015), \url{https://cds.cern.ch/record/2020886}

\bibitem{bib:masterclass}
The International Particle Outreach Group home page, that includes information on the International Masterclasses, is found on the web site \url{http://www.physicsmasterclasses.org/index.php}.

\bibitem{bib:EYH}
The information on the Expanding Your Horizon Network can be found at the 
organization's home page \url{http://www.eyhn.org}.


\bibitem{bib:artcms} \url{https://artcms.web.cern.ch}

\bibitem{bib:DASPOS}
\url{http://daspos.crc.nd.edu}

\bibitem{bib:speakers} \url{http://speakersbureau.unl.edu}

\end{thebibliography}



