\begin{thebibliography}{99}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
%%% EVERYTHING BELOW IS OLD, REVIEW AND KEEP AS NEEDED}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5




%
% THIS ITEM BELOW IS JUST A STARTER, REMOVE IT WHEN IT IS NOT NEEDED
%
% \bibitem{bib:CMSHiggs} CMS Collaboration, ``Observation of a new boson at a
%   mass of 125~GeV with the CMS experiment at the LHC,'' Phys. Lett. {\bf
%     B716} 30 (2012), \url{http://dx.doi.org/10.1016/j.physletb.2012.08.021}

\bibitem{bib:P5}
Particle Physics Project Prioritization Panel, ``Building for Discovery - Executive Summary,'' (2014), \url{http://go.unl.edu/8oyk}
%
% Top papers
%
\bibitem{bib:single-top-papers}
CMS Collaboration, ``Observation of the associated production of a single top quark and a W boson in pp collisions at $\sqrt{s}=$8\TeV,'' Phys. Rev. Lett. 112 (23), 231802 (2014), \url{http://doi.org/10.1103/PhysRevLett.112.231802};
%
CMS Collaboration, ``Measurement of the t-channel single-top-quark production cross section and of the $|V_{tb}|$ CKM matrix element in pp collisions at $\sqrt{s} = 8$\TeV,'' Journal of High Energy Physics 06 (2014) 090, \url{http://doi.org/10.1007/JHEP06(2014)090};
%
CMS Collaboration, ``Measurement of the W boson helicity in events with a
single reconstructed top quark in pp collisions at $\sqrt{s}=$8\TeV,''
Journal of High Energy Physics 01 (2015) 053,
\url{http://doi.org/10.1007/JHEP01(2015)053}.
%
\bibitem{bib:tracker-top-mass}
 CMS Collaboration, ``Measurement of the top quark mass using charged
 particles in pp collisions at $\sqrt{s} = 8$\TeV,'' Phys. Rev.  D93 092006
 (2016), \url{http://doi.org/10.1103/PhysRevD.93.092006}. 
%
% Higgs papers
%
\bibitem{bib:HWWlegacy}
    CMS Collaboration, ``Measurement of Higgs boson production and properties in the WW decay channel with leptonic final states,''
    Journal of High Energy Physics 01 (2014) 096, \url{http://doi.org/10.1007/JHEP01(2014)096}.
%
\bibitem{bib:higgs-spin-parity}
  CMS Collaboration, ``Constraints on the spin-parity and anomalous HVV couplings of the Higgs boson in proton collisions at 7 and 8 TeV,''
  Phys. Rev. D92 012004 (2015), \url{http://doi.org/10.1103/PhysRevD.92.012004}.
%
\bibitem{bib:HWW-pT}
    CMS Collaboration, ``Measurement of the transverse momentum spectrum of the Higgs boson produced in pp collisions at sqrt(s) = 8 TeV using H to WW decays,'' Journal of High Energy Physics 03 (2017) 032, \url{http://doi.org/10.1007/JHEP03(2017)032}.
%
\bibitem{bib:Higgs-width}
    CMS Collaboration, ``Search for Higgs boson off-shell production in proton-proton collisions at 7 and 8 TeV and derivation of constraints on its total decay width,'' Journal of High Energy Physics 09 (2016) 051, \url{http://doi.org/10.1007/JHEP09(2016)051}.
%
% Top-Higgs references
%
\bibitem{bib:tHqbbPAS} CMS Collaboration, ``Search for $H \to b\bar{b}$ in
  association with single top quarks as a test of Higgs boson couplings,'' CMS PAS HIG-14-015 (2015), \url{https://cds.cern.ch/record/1952829}.
%
\bibitem{bib:tHqRun1} CMS Collaboration, ``Search for the associated
  production of a Higgs boson with a single top quark in proton-proton
  collisions at $sqrt{s} = 8$\TeV,'' Journal of High Energy Physics 06 (2016) 177, \url{doi.org/10.1007/JHEP06(2016)177}.
  %%% \url{http://arxiv.org/abs/1509.08159}.
%
\bibitem{bib:monroy_thesis} Jose Andres Monroy Montanez, ``Search for production of a Higgs boson and a single top quark in multilepton final states in pp collisions at $\sqrt{s} = 13$~TeV,'' Ph.D. dissertation, CERN-THESIS-2018-161, \url{http://cds.cern.ch/record/2639240}.
%
\bibitem{bib:tHqRun2PAS} CMS Collaboration, ``Search for the associated
    production of a Higgs boson and a single top quark in $pp$ collisions
    at $\sqrt{s} = 13$\TeV,'' CMS PAS HIG-18-009 (2018),
    \url{https://cds.cern.ch/record/2628662}.
%
\bibitem{bib:tHqRun2} CMS Collaboration, ``Search for the associated
    production of a Higgs boson and a single top quark in $pp$ collisions
    at $\sqrt{s} = 13$\TeV,'' FILL IN PUB INFO WHEN READY.
%
\bibitem{bib:ttHmultilep} CMS Collaboration, ``Search for $t\bar{t}H$
  production in multilepton final states at $\sqrt{s} = 13$\TeV, CMS PAS
  HIG-15-008 (2015), \url{https://cds.cern.ch/record/2141078}.
%
% Standard model precision 
%
\bibitem{bib:DY7}
    CMS Collaboration, ``Measurement of the differential and double-differential Drell-Yan cross sections in proton-proton collisions at $\sqrt{s}=$7~TeV,''
    Journal of High Energy Physics 12 (2013) 030, \url{http://doi.org/10.1007/JHEP12(2013)030}.
%
\bibitem{bib:DY8}
    CMS Collaboration, ``Measurements of differential and double-differential Drell-Yan cross sections in proton-proton collisions at $sqrt{s}=$8~TeV,''
    European Physics Journal {\bf C75} (2015) 147, \url{http://doi.org/10.1140/epjc/s10052-015-3364-2}.
%
\bibitem{bib:DY13}
    CMS Collaboration, ``Measurement of the differential Drell-Yan cross section in proton-proton collisions at 13 TeV,'' 
    CMS PAS SMP-16-009 (2016), \url{http://cds.cern.ch/record/2205152}.
%
%
% New physics references
%
\bibitem{bib:higgs-LFV}
 CMS Collaboration, ``Search for lepton-flavour-violating decays of the Higgs boson, '' Phys. Lett. {\bf B749} 337 (2015), \url{http://doi.org/10.1016/j.physletb.2015.07.053}.
%
\bibitem{bib:quark-compositness-etc}
CMS Collaboration, ``Search for quark contact interactions and extra spatial dimensions using dijet angular distributions in proton–proton collisions at $\sqrt{s}$8\TeV,'' Phys. Lett. {\bf B746} 79 (2015), \url{http://doi.org/10.1016/j.physletb.2015.04.042}.
%
\bibitem{bib:bstar}
CMS Collaboration, ``Search for the production of an excited bottom quark decaying to tW in proton-proton collisions at $\sqrt{s} = 8\TeV$,'' Journal of High Energy Physics 01 (2016) 166,  \url{https://doi.org/10.1007/JHEP01(2016)166}.
%%% \url{http://arxiv.org/abs/1509.08141}
%
% Computing references
%
\bibitem{bib:resource-modeling}  See
  \url{https://github.com/kenbloom/resource-modeling}.
  %
\bibitem{bib:AAA} K.~Bloom, T.~Boccali, B.~Bockelman, D.~Bradley, S.~Dasu,
  J.~Dost, F.~Fanzago, I.~Sfiligoi, A.~Mrak Tadel, M.~Tadel, C.~Vuosalo,
  F.~W{\"u}rthwein, A.~Yagil and M.~Zvada, ``Any Data, Any Time, Anywhere:
  Global Data Access for Science,'' 2015 IEEE/ACM 2nd International
  Symposium on Big Data Computing (BDC), Limassol, pp. 85-91 (2015),
  \url{https://arxiv.org/abs/1508.01443}, \url{http://doi.org/10.1109/BDC.2015.33}.
%
\bibitem{bib:hepcloud} B.~Holzman, L.A.T.~Bauerdick, B.~Bockelman, D.~Dykstra, I.~Fisk, S.~Fuess, G.~Garzoglio, M.~Girone, O.~Gutsche, D.~Hufnagel, H.~Kim, R.~Kennedy, N.~ Magini, D.~Mason, P.~Spentzouris, A.~Tiradani, S.~Timm, E.W.~Vaandering, ``HEPCloud, a New Paradigm for HEP Facilities: CMS Amazon Web Services Investigation,''
Comput. Softw. Big Sci. (2017) 1: 1, \url{https://doi.org/10.1007/s41781-017-0001-9}.
%
\bibitem{bib:MONIT} {\bf Find a MONIT reference if possible.}
%
% Other
%
\bibitem{bib:alignment}
CMS Collaboration, ``Alignment of the CMS tracker with LHC and cosmic ray data,'' J.~Instrum. \textbf{9} (2014) P06009, 
\url{http://doi.org/10.1088/1748-0221/9/06/P06009}.
%%% \url{http://arxiv.org/abs/1403.2286}.
%
\bibitem{bib:EGM-Run1}
CMS Collaboration, ``Performance of electron reconstruction and selection with the CMS detector in proton-proton collisions at $\sqrt{s}=$8~TeV,'' J. Instrum. {\bf 10} (2015) P06005, \url{http://doi.org/10.1088/1748-0221/10/06/P06005}.
%
\bibitem{bib:EGM-Run2-DP}
    CMS Collaboration, ``Electron and Photon performance in CMS with the data sample collected in 2016-17-18 at 13 TeV for the ICHEP 2018 Conference,''
    CMS Detector Performance Summaries CMS-DP-2018-041, \url{https://cds.cern.ch/record/2629363}.
%
% Greg's reference, commented out
%\bibitem{bib:thesisawardwebsite} \url{http://cmsthesisawards.web.cern.ch}
%
% Greg's reference, commented out
%\bibitem{bib:portfolioreview} For more information on this review, see the review summary presented at %\url{https://science.energy.gov/~/media/hep/hepap/pdf/201804/Montgomery_HEPAP_201805.pdf}.
%
\bibitem{bib:D0afb} 
D0 Collaboration, ``Measurement of the forward-backward asymmetry in the distribution of leptons in $t\bar{t}$ in the lepton+jets channel,'' Phys. Rev. {\bf D90} 072001 (2014), \url{http://doi.org/10.1103/PhysRevD.90.072001};
D0 Collaboration, ``Measurement of the forward-backward asymmetry in top quark-antiquark production in $p\bar{p}$ collisions using the lepton+jets channel,'' Phys. Rev. {\bf D90} 072011 (2014), \url{http://doi.org/10.1103/PhysRevD.90.072011};
D0 Collaboration, ``Simultaneous measurement of forward-backward asymmetry and top polarization in dilepton final states from $t\bar{t}$ production at the Tevatron,'' Phys. Rev. {\bf D92} 052007 (2015), \url{http://doi.org/10.1103/PhysRevD.92.052007};
CDF Collaboration and D0 Collaboration, ``Combined Forward-Backward Asymmetry Measurements in Top-Antitop Quark Production at the Tevatron'' Phys. Rev. Lett 120 (4), 042001 (2018), \url{https://doi.org/10.1103/PhysRevLett.120.042001}.
%
% Outreach
%
\bibitem{bib:noyce}
E. ~B. ~Lewis, A. ~A. ~Musson, J. ~Lu, Lewis, E.B., `` Educating Highly-qualified Science Teachers: Challenges and Perspectives,” National Association for Research in Science Teaching (NARST 2014) Proceedings, Pittsburgh, PA, Volume: 87; 
E. ~B. ~Lewis, A. ~A. ~Musson, R. ~McCarty, `` Evaluating a Graduate-level Science Teacher Education Program,” the Association for Science Teacher Education 2014 (ASTE 2014) International Conference Proceedings.
%
\bibitem{bib:bloomblog} \url{http://www.quantumdiaries.org/author/ken-bloom/}.
%
\bibitem{bib:TBBTQD} \url{http://www.quantumdiaries.org/2015/02/05/theory-and-experiment-come-together-bazinga/}.
%
\bibitem{bib:TBBTepisode} \url{http://bit.ly/16NhxDu}
%
\bibitem{bib:BloomFNALToday} See for example \url{http://news.fnal.gov/2016/08/ichep-race-condition/} and \url{http://news.fnal.gov/2017/06/my-first-day-fermilab-my-first-fermilab-id/}.
%
\bibitem{bib:BloomAAPT} \url{https://www.aapt.org/Conferences/wm2017/}
%
\bibitem{bib:LHCSeason2} See \url{https://youtu.be/nsR7nZNKqoo}.
%
\bibitem{bib:speakers} \url{http://speakersbureau.unl.edu}
%
\bibitem{bib:tH_theory} F.~Demartin, F.~Maltoni, K.~Mawatari, and M.~Zaro,
  ``Higgs production in association with a single top quark at the LHC,''
  European Physical Journal {\bf C75}, 267
  (2015). \url{https://doi.org/10.1140/epj c/s10052-015-3475-9};
  F.~Demartin, B.~Maier, F.~Maltoni, K.~Mawatari, and M.~Zaro, ``tWH
  associated production at the LHC'', European Physical Journal {\bf C77}, 34 (2017)
  \url{http://doi.org/10.1140/epjc/s10052-017-4601-7}. 
  %%% arXiv:1607.05862
%
% Di-Higgs
%
\bibitem{bib:radion-graviton-CMS}
    CMS Collaboration, ``Search for resonant and nonresonant Higgs boson pair production in the bblnulnu final state in proton-proton collisions at sqrt(s) = 13 TeV,'' 
    Journal of High Energy Physics 01 (2018) 054, \url{http://doi.org/10.1007/JHEP01(2018)054}.
%
\bibitem{bib:radion-graviton-ATLAS}
    ATLAS Collaboration, ``Search for Higgs boson pair production in the $\gamma\gamma b\overline{b}$ final state with 13 TeV pp collision data collected by the ATLAS experiment,''
    Journal of High Energy Physics 11 (2018) 040, \url{https://doi.org/10.1007/JHEP11(2018)040}.
%
\bibitem{bib:HH-benchmarks}
    A.~Carvalho, M.~Dall’Osso, T.~Dorigo, F.~Goertz, C.~A.~Gottardo, M.~Tosi,
    ``Higgs pair production: choosing benchmarks with cluster analysis,''
    Journal for High Energy Physics 04 (2016) 126, \url{http://doi.org/10.1007/JHEP04(2016)126}.
%
%
%
\bibitem{bib:HHproduction_theory} R.~Frederix, S.~Frixione, V.~Hirschi,
  F.~Maltoni, O.~Mattelaer, P.~Torrielli, E.~Vryonidou, M.~Zaro, ``Higgs
  pair production at the LHC with NLO and parton shower effects,''
  Phys. Lett. {\bf B732} 142 (2014), \url{ https://doi.org/10.1016/j.physletb.2014.03.026}.
\bibitem{bib:Higgs-width-tttt}
    Q.-H.~Cao, S.-L.~Chen, Y.~Liu,
    ``Probing Higgs width and top quark Yukawa coupling from $t\overline{t}H$ and $t\overline{t}t\overline{t}$ productions,''
    Phys. Rev. {\bf D95} 053004 (2017), \url{http://doi.org/10.1103/PhysRevD.95.053004}.

%
\bibitem{bib:ATLAS-3D}
    ATLAS Collaboration, ``Measurement of the Drell-Yan triple-differential cross section in pp collisions at $\sqrt{s}=$8~TeV,''
    Journal of High Energy Physics 12 (2017 059, \url{http://doi.org/10.1007/JHEP12(2017)059}.
%
\bibitem{bib:Phase2TDR}
CMS Collaboration, ``The Phase-2 Upgrade of the CMS Tracker,'' CERN-LHCC-2017-009 (2017),
\url{https://cds.cern.ch/record/2272264}.
%
\bibitem{bib:teacherdevelopment} M.~Baquerizo Birth, D.~Claes, J.~Pederson, ``Physics Teacher as Physics Expert: Research Participation as Professional Development,''  The Science Educator {\bf 26} (2018).
\end{thebibliography}
